Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-10-31 paper.tex
update

However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered, rather than a fully automated method. And only cost and time are considered in the optimised problems. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising a weighed graph representation as the particles in the PSO.

>>>>

However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology. Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method. In QoS, only cost and time are considered in the optimised problems. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.
